---
title: Completely Randomized Design with More than One Treatment Factor
teaching: 0
exercises: 0
source: Rmd
---

::::::::::::::::::::::::::::::::::::::: objectives

- .
- .

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- How is a CRD with more than one treatment factor designed and analyzed?

::::::::::::::::::::::::::::::::::::::::::::::::::

experiment structured by two or more factors that can be qualitative or quantitative. Same design issues - which factors to choose, which levels? A full factorial experiment includes all levels of all factors,
which can become unwieldy when there are many levels for each factor. There are options to use only a fraction of the factor levels. Let's consider full factorial experiment here.

```{r, include=FALSE}

```


```{r explore_data}
drugExercise <- read.csv("data/drugExercise.csv")

drugExercise %>% 
  group_by(Exercise, DrugDose) %>% 
  summarise(mean = mean(Glucose))

drugExercise %>% 
  group_by(DrugDose, Exercise) %>% 
  summarise(mean = mean(Glucose))

drugExercise %>% 
  ggplot(aes(Exercise, Glucose)) + 
  geom_point(aes(color = DrugDose))

drugExercise %>% 
  ggplot(aes(DrugDose, Glucose)) + 
  geom_point(aes(color = Exercise))

# Interaction plot
interaction.plot(x.factor = data$DrugDose,
                 trace.factor = data$Exercise,
                 response = data$Glucose,
                 fun = mean,
                 col = hcl.colors(4),
                 xlab = "Drug Dose (mg/kg)",
                 ylab = "Mean Blood Glucose (mg/dL)",
                 trace.label = "Exercise Duration (min)")
```

If lines were parallel we could assume no interaction. Since they are not 
parallel we should assume interaction between exercise and drug dose.

```{r anova}
anova(lm(Glucose ~ DrugDose + Exercise + DrugDose*Exercise, 
         data = drugExercise))
```

:::::::::::::::::::::::::::::::::::::::: keypoints

- Completely randomized designs can be structured with two or more factors.
- Random assignment of treatments to experimental units in a single homogeneous group is the same.
- Factorial structure of the experiment requires different analyses, primarily
ANOVA.

::::::::::::::::::::::::::::::::::::::::::::::::::


