---
title: Completely Randomized Design with More than One Treatment Factor
teaching: 0
exercises: 0
source: Rmd
---

::::::::::::::::::::::::::::::::::::::: objectives

- .
- .

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- How is a CRD with more than one treatment factor designed and analyzed?

::::::::::::::::::::::::::::::::::::::::::::::::::

When experiments are structured with two or more factors, these factors can be
qualitative or quantitative. With two or more factors we face the same design
issues. Which factors to choose? Which levels for each factor? A full factorial
experiment includes all levels of all factors, which can become unwieldy when
there are multiple levels for each factor. One option to manage an unwieldy 
design is to use only a fraction of the factor levels in a fractional factorial
design. In this lesson we consider a full factorial design containing all levels
of all factors.

```{r, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

A study aims to determine how dosage of a hypoglycemic drug and duration of 
daily exercise affect blood glucose levels in diabetic mice. The study has two 
quantitative factors with four levels each.

```{r, study_design, include=FALSE}
studyDesign <- tibble("Drug dosage (mg/kg)" = c("0 (control)", 5, 10, 20),
                      "Exercise duration (min/day)" = c("0 (sedentary control)",
                                                        15, 30, 60))
knitr::kable(studyDesign)
```

Drug dosage represents the amount of a new antidiabetic drug administered daily.
The levels for this factor are in mg per kg body weight. Control mice receive no
drug. The second factor, exercise duration, represents the number of minutes the 
mice run on a running wheel each day. Control mice do not have a running wheel 
to run on. A full factorial design is used, with each combination of drug dosage 
and exercise duration applied to a group of mice. For example, one group 
receives 5 mg/kg of the drug and exercises 15 minutes per day, another group
receives 5 mg/kg and exercises 30 minutes per day, and so on.

There are 4 levels for each factor, leading to 16 treatment combinations (4 drug 
doses × 4 exercise durations). Each combination is replicated with a group of 5 
mice, making the design balanced and allowing analysis of interactions. Fasting 
blood glucose level (mg/dL) was measured at the start and after 4 weeks of
treatment.

```{r explore_data, message=FALSE}
drugExercise <- read_csv("data/drugExercise.csv")
drugExercise$DrugDose <- as_factor(drugExercise$DrugDose)
drugExercise$Exercise <- as_factor(drugExercise$Exercise)

# drugExercise %>%
#   group_by(Exercise, DrugDose) %>%
#   summarise(ChangeGlucose = mean(Delta))

drugExercise %>%
   group_by(DrugDose, Exercise) %>%
  summarise(ChangeGlucose = mean(Delta))

heat_data <- drugExercise %>%
  group_by(DrugDose, Exercise) %>%
  summarise(MeanChange = mean(Delta), .groups = "drop") %>%
  spread(Exercise, MeanChange)
heat_matrix <- as.matrix(heat_data[,-1])
rownames(heat_matrix) <- heat_data$DrugDose
heatmap(heat_matrix, Rowv = NA, Colv = NA,
        col = heat.colors(10), scale = "none",
        main = "Heatmap of Mean Δ Glucose",
        xlab = "Exercise (minutes)", ylab = "Drug Dosage (mg/kg)")

ggplot(drugExercise, aes(x = DrugDose, y = Delta, fill = Exercise)) +
  geom_boxplot() +
  labs(title = "Change in Glucose by Drug and Exercise",
       y = "Δ Glucose (mg/dL)", x = "Drug Dosage (mg/kg)")

ggplot(drugExercise, aes(x = Exercise, y = Delta, fill = DrugDose)) +
  geom_boxplot() +
  labs(title = "Change in Glucose by Drug and Exercise",
       y = "Δ Glucose (mg/dL)", x = "Exercise duration (min/day)")

ggplot(drugExercise, aes(x = Baseline, y = Post, color = DrugDose)) +
  geom_point(aes(shape = Exercise), size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Baseline vs Post-treatment Glucose",
       x = "Baseline Glucose (mg/dL)",
       y = "Post-treatment Glucose (mg/dL)") +
  theme_minimal()

drugExercise %>% 
  ggplot(aes(Exercise, Delta)) + 
  geom_point(aes(color = DrugDose))

drugExercise %>% 
  ggplot(aes(DrugDose, Delta)) + 
  geom_point(aes(color = Exercise))
```

## Interaction between factors
We could analyze these data as if it were simply a completely randomized design
with 16 treatments (4 drug doses and 4 exercise durations). The ANOVA would have 
15 degrees of freedom for treatments and the F-test would tell us whether the 
variation among average changes in glucose levels for the 16 treatments was real 
or random. However, the factorial treatment structure lets us separate out the 
variability in glucose level changess among drug doses averaged over exercise 
durations. The ANOVA table would provide a sum of squares based on 3 degrees of 
freedom for the difference between the 4 treatment means ($\bar{y}_i$) and the 
pooled (overall) mean ($\bar{y}$).  

Sum of squares for 16 treatments $= n\sum(\bar{y}_i - \bar{y})^2$. 

The sum of squares would capture the variability among the 4 drug dose levels.
The variation among the 4 exercise levels would be captured similarly, with 3
degrees of freedom. That leaves 15 - 6 = 9 degrees of freedom left over. What 
variability do these remaining 9 degrees of freedom contain? The answer is
interaction - the interaction between drug doses and exercise durations. Mean 
changes in glucose for each of the 16 treatments is given in the table below.

```{r means_table, echo=FALSE, message=FALSE}
means <- drugExercise %>%
  group_by(Exercise, DrugDose) %>%
  summarise(meanChange = round(mean(Delta), 1))

knitr::kable(pivot_wider(means, 
                         names_from = DrugDose, 
                         values_from = meanChange)) %>% 
  add_header_above(c(" " = 2, "Drug Dose" = 3))
```

We can visualize interactions for all combinations of drug dose and exercise 
duration with an interaction plot that shows mean change in glucose levels.

```{r interaction1}
# Interaction plot
interaction_plot <- drugExercise %>%
  group_by(DrugDose, Exercise) %>%
  summarise(MeanChange = mean(Delta), .groups = "drop")

ggplot(interaction_plot, aes(x = as.numeric(as.character(DrugDose)),
                             y = MeanChange,
                             color = Exercise, group = Exercise)) +
  geom_line() +
  geom_point() +
  labs(title = "Interaction Plot",
       x = "Drug Dosage (mg/kg)",
       y = "Mean Δ Glucose (mg/dL)")
```

The interaction plot shows wide variation in mean glucose changes at a drug dose 
of 20 mg/kg. For the 0 and 15 minute/day exercise groups, increasing drug dosage
led to decreasing mean glucose levels. For the 30 and 60 minute/day exercise 
groups, increasing drug dosage did not decrease mean glucose levels appreciably, 
with one exception. At 5 mg/kg doseage, The 60 minute/day exercise group saw a 
strong decrease in mean blood glucose.

```{r interaction2}
ggplot(interaction_plot, aes(x = as.numeric(as.character(Exercise)),
                             y = MeanChange,
                             color = DrugDose, group = DrugDose)) +
  geom_line() +
  geom_point() +
  labs(title = "Interaction Plot",
       x = "Exercise (min/day)",
       y = "Mean Δ Glucose (mg/dL)")
```

If we plot exercise on the x-axis, the same patterns show up differently. This 
second interaction plot shows wide variation in mean glucose changes at a drug 
dose of 20 mg/kg. For the other drug dose groups (0, 5 and 10 mg/kg), mean 
glucose changes are nearly the same for the 60 minute/day exercise group. At 5 
mg/kg doseage, the 60 minute/day exercise group saw a strong decrease in mean 
blood glucose.
If lines were parallel we could assume no interaction between drug and exercise. 
Since they are not  parallel we should assume interaction between exercise and 
drug dose. The F-test from an ANOVA will tell us whether this apparent 
interaction is real or random, specifically whether it is more pronounced than 
would be expected due to random variation.

```{r anova}
# DrugDose*Exercise is the interaction
anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, 
         data = drugExercise))

```

We can read the ANOVA table from the bottom up, starting with the interaction
(`DrugDose:Exercise`). The `F value` for the interaction is 
`r round(anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[3, 4], 1)`
on 
`r anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[3, 1]`
and 
`r anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[4, 1]`
degrees of freedom for the interaction and error (`Residuals`) respectively. The 
p-value (`Pr(>F)`) is near very low and as such the interaction between exercise 
and drug dose is significant, backing up what we see in the interaction plots. 
If we move up a row in the table to `Exercise`, the F test compares the mean 
changes across drug dose groups. The `F value` for exercise is 
`r round(anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[2, 4], 1)`
on 
`r anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[2, 1]`
and 
`r anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[4, 1]`
degrees of freedom for exercise and residuals respectively. The p-value  is high 
at
`r round(anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[2, 5], 3)`
and is significant. Finally, we move up to the row containing `DrugDose` to
find an F value of 
`r round(anova(lm(Delta ~ DrugDose + Exercise + DrugDose*Exercise, data = drugExercise))[1, 4], 1)`
and a very low p-value again. Drug dose averaged over exercise is significant.  
The partitioning of treatments sums of squares into main effect (average) and 
interaction sums of squares is a result of the crossed factorial structure of 
the two factors. The development of efficient and informative multifactor 
designs that provide clean partitioning between main effects and interactions
is one of the most important contributions of statistical experimental design.

:::::::::::::::::::::::::::::::::::::::: keypoints

- Completely randomized designs can be structured with two or more factors.
- Random assignment of treatments to experimental units in a single homogeneous group is the same.
- Factorial structure of the experiment requires different analyses, primarily
ANOVA.

::::::::::::::::::::::::::::::::::::::::::::::::::


